\Huge Conferences in an Era of Expensive Carbon

### 2019-06-20 main.tex
Small changes.

How should ACM respond to these facts?  We have two concrete
proposals. First, all ACM conferences should publicly {\em account} for CO2e
emitted as a result of putting them on. Second, ACM should put a
\emph{price} on carbon in conference budgets, to create pressure on
organizers to reduce their footprints.

@@

Another simple, short-term expedient for lowering net the emissions
footprint of conferences is purchasing \emph{carbon
  offsets}~\cite{CarbonOFfsetReport}.
%
A carbon offset is sold by a vendor who uses the raised funds to finance an
activity that permanently avoids emitting some amount of greenhouse gases.
The veracity and permanence of this CO2e emission avoidance is certified by
a watchdog organization. (Typically, planting trees is not a certifiable
activity, since it's hard to guarantee the trees won't be cut down, but
installing methane capture devices on landfill sites or buying
fuel-efficient stoves to replace open-fire cooking in poor communities can
be.)
%
Many organizations, including companies such as Google, Dell, Microsoft,
General Motors, Delta Airlines, Lyft, and Expedia, numerous universities,
and some academic societies, now buy carbon offsets in order to reduce their
net footprint. ACM conferences can do the same, and the purchases can be
included in the public accounting we are proposing.  In fact, ACM recently
decided to allow conferences to allow attendees to pay for an offset during
registration; the conference then uses the designated funds to purchase the
offset from a qualified vendor.  Some conferences are also experimenting
with corporate sponsorship of bulk offsets for the whole conference.  (It
should be noted that carbon offsets are a controversial tool.  Besides
issues with verifiability and permanence, some observers worry
that---especially given their currently quite low cost---they will encourage
complacency, leading organizations to postpone making the difficult changes
that will certainly be required to fully decarbonize society.  We agree that
offsets are at best a short-term measure, to be considered in parallel with,
not instead of, more difficult cutting.)

@@

ACM can provide tools for gathering and publicizing this data. As a start,
SIGPLAN (the special interest group on programming languages) recently
worked with ACM's SIG Governing Board to develop an air-travel-focused CO2e
calculator for conferences. Users can upload conference registration data,
and the calculator will estimate the CO2e cost of air travel for those
sufficiently far away. This calculator could be expanded to account for
other conference emissions.

@@

However, while publicly accounting for CO2e expenditures will incentivize
some CO2e reductions, it will probably not, by itself, induce major changes
to the conference system.  There are good reasons for this, since such
changes will undoubtedly impact the value that conferences provide.
%
Science is a fundamentally social process, and the conference system
accelerates scientific research through high-bandwidth interaction,
direct dissemination of results, network building, and serendipitous
cross-fertilization.
%
Organizers and attendees will be reticent to make changes that could
harm the scientific benefits they have all regularly experienced.

@@

Ideally, at some point, governments will impose carbon pricing uniformly,
and all CO2e-intensive activities will have to pay it. But ACM can send a
strong message about the importance of this issue by acting now. In
particular, as several companies have shown, even an artificial ``internal
price'' on carbon creates a significant price signal that shapes behavior.
%
Thus, our second (more ambitious) proposal is: ACM should impose a a
surcharge on conferences based on their carbon footprint.  The charge should
be low at the beginning and increase steadily (and predictably) year on
year.
%
Conference organizers can then choose (on the basis of careful analysis of
data and weighing of benefits) how best to balance their budgets---whether
by decreasing emissions, increasing registration fees, soliciting additional
corporate sponsorship, or some combination.

What should ACM do with the funds collected from this surcharge?  One can
imagine many good uses, including buying carbon
offsets~\cite{CarbonOFfsetReport}, supporting ``green'' computing
research\bcp{can we mention some specifics?}, and defraying the costs of
virtualizing conferences (livestreaming, etc.).  \bcp{Expand this paragraph
  a bit.}

>>>>

How should ACM respond to these facts? We are the members of SIGPLAN's
(the special interest group on programming languages) Climate
Committee,\footnote{https://www.sigplan.org/Resources/Climate/} and we
have been researching this 
question for the past couple of years. Our work has led to two concrete
proposals. First, all ACM conferences should publicly {\em account} for CO2e
emitted as a result of putting them on. Second, ACM should put a
\emph{price} on carbon in conference budgets, to create pressure on
organizers to reduce their footprints.

@@

SIGPLAN has also been exploring how to mitigate a conference's CO2e emissions
by purchasing \emph{carbon
  offsets}~\cite{CarbonOFfsetReport}.
%
A carbon offset is sold by a vendor who uses the raised funds to finance an
activity that permanently avoids emitting some amount of greenhouse gases.
The veracity and permanence of this CO2e emission avoidance is certified by
a watchdog organization. (Typically, planting trees is not a certifiable
activity, since it's hard to guarantee the trees won't be cut down, but
installing methane capture devices on landfill sites or buying
fuel-efficient stoves to replace open-fire cooking in poor communities can
be.)
%
Many organizations, including companies such as Google, Dell, Microsoft,
General Motors, Delta Airlines, Lyft, and Expedia, numerous universities,
and some academic societies, now buy carbon offsets in order to reduce their
net footprint. ACM conferences can do the same, and the purchases can be
included in the public accounting we are proposing.  In fact, ACM recently
decided that conferences could offer attendees the option to pay for an offset during
registration; the conference then uses the designated funds to purchase the
offset from a qualified vendor.  Some conferences are also experimenting
with corporate sponsorship of bulk offsets for the whole conference.\footnote{It
should be noted that carbon offsets are a controversial tool.  Besides
issues with verifiability and permanence, some observers worry
that---especially given their currently artificially-low cost---they will encourage
complacency, leading organizations to postpone making the difficult changes
that will be required to sustainably decarbonize society.  We believe that
offsets are a short-term measure, to be considered in parallel with,
not instead of, more difficult cutting.}

@@

ACM can provide tools for gathering and publicizing this data. As a start,
SIGPLAN recently
worked with ACM's SIG Governing Board to develop an air-travel-focused CO2e
calculator for conferences. Users can upload conference registration data,
and the calculator will estimate the CO2e cost of air travel for those
sufficiently far away. This calculator could be expanded to account for
other conference emissions.

@@

While publicly accounting for CO2e expenditures will incentivize
some CO2e reductions, it will probably not, by itself, induce major changes
to the conference system. 
%
Science is a fundamentally social process, and the conference system
accelerates scientific research through high-bandwidth interaction,
direct dissemination of results, network building, and serendipitous
cross-fertilization.
%
Organizers and attendees will be reticent to make changes that could
harm the scientific benefits they have all regularly experienced.

@@

Ideally, at some point, governments will impose carbon pricing uniformly,
and all CO2e-intensive activities will have to pay it. But ACM can send a
strong message about the importance of this issue by acting now. In
particular, as several companies have shown, even an artificial ``internal
price'' on carbon creates a significant price signal that shapes behavior.
%
Thus, our second (more ambitious) proposal is: ACM should impose a a
surcharge on conferences based on their carbon footprint.  The charge should
be low at the beginning and increase steadily (and predictably) year on
year.
%
Conference organizers can then choose (on the basis of careful analysis of
data and weighing of benefits) how best to balance their budgets---whether
by decreasing emissions, increasing registration fees, soliciting additional
corporate sponsorship, or some combination. \mwh{Problem: We showed
  just above that it's hard to figure out what to do. Come back to
  this point here and say that the surcharge will spur bold choices?
  Maybe say that these choices won't necessarily be bad, but could be
  really great?}

What should ACM do with the funds collected from this surcharge?  One can
imagine many good uses, including buying carbon
offsets, supporting ``green'' computing
research\bcp{can we mention some specifics?}, and defraying the costs of
virtualizing conferences (livestreaming, etc.).  \bcp{Expand this paragraph
  a bit.}
